Computer Science House By-Laws

### 2017-10-30 bylaws.tex
Scale directorship meeting requirement by semester

\bsection{Expectations of House Members}
Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings, and attend at least twenty-five (25) of the permanent director meetings.
\\* \\*
The member must participate significantly in at least one major project during the academic year.
The member is required to submit a description for this major project to the Executive Board for approval.
As an option to this requirement, the member may instead assist on a large number of House activities and projects.
However, it is to be understood in advance by the member that this option requires a great deal of participation throughout the year.
This participation will be evaluated by the Executive Board.

>>>>

\bsection{Expectations of House Members}
Each member is required to pay House dues as stated in \ref{Collection of House Dues}, attend all House Meetings, and attend at least fifteen (15) of the House directorship meetings (including permanent and Ad-Hoc directorship meetings) for each Academic Semester in which they are an Active Member.
\\* \\*
The member must participate significantly in at least one major project during the academic year.
The member is required to submit a description for this major project to the Executive Board for approval.
As an option to this requirement, the member may instead assist on a large number of House activities and projects.
However, it is to be understood in advance by the member that this option requires a great deal of participation throughout the year.
This participation will be evaluated by the Executive Board.
